Solar wind prediction for the Parker Solar Probe orbit

### 2017-06-24 paperMVVB/sections/content.tex
minor change

%difference to other models
There are many studies analyzing the solar wind dependence on solar activity and heliocentric distance with Helios data (\citet{Schwenn1983, Bougeret1984, Schwenn1990}). They examine average values, additionally distinguishing between slow and fast wind. In this paper we instead look at the variations of the bulk frequency distributions, consider solar activity and extrapolate these to the near-Sun region.\\

>>>>

This paper examines the variations of the bulk solar wind frequency distributions, considers solar activity and extrapolates these distributions to the near-Sun region.\\
